Measuring individual differences in the understanding of gaze cues across the lifespan

### 2022-02-18 paper/manuscript.Rmd
create rough paper structure

# Introduction 
Idea for an opener :)

@@

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material
Material is presented as an interactive web-app that is accessible for computers and tablets and runs on any web browser. The code is open-source (https://github.com/ccp-eva/gafo-demo) and a live demo version can be found under: https://ccp-odc.eva.mpg.de/gafo-demo/.

@@

## Procedure
In the beginning of the online study, families were invited to enter "our virtual institute" and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure. Then, caregivers were informed about data security and were asked for their informed consent. They were asked to enable the sound and seat their child centrally in front of their device. Subsequently, a brief demographic questionnaire was displayed, asking for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in day care, and if yes, (5) since when and (6) for how long on an average day. Before the study started, families were instructed how to setup their webcam and enable the recording permissions. Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves. 
Then, families were guided through the online study with pre-recorded audio instructions. After completion, families received a little crafting / coloring sheet as a small thank-you gift.

## Stimuli
An animal character (i.e., agent; sheep, monkey, or pig) is placed centrally in a window. A balloon (i.e., target; blue, green, yellow, or red) is located in front of them. The target then falls to the ground. The agent’s gaze tracks the movement of the target, that is, the pupils and iris of the agent move in a way that their center aligns with the center of the target. Participants were then asked to locate the target’s position on the screen.

There are three different trial types, depending on the visual access to the target flight and end location. In *touch training* trials, participants have *full visual access* to the target flight and the target's end location. In *familiarization trials*, participants have *partial visual access*: they witness the target flight but cannot see the target's end location. In *test trials*, participants have *no visual access* to the target flight nor the end location. When partial or no information about the target location is accessible,  participants are expected to use the agent’s gaze as a cue.

### Remote datacollection
Depending on the participant's device, the website automatically presents the hedge or box version of the study. For families that use a tablet with touchscreen, the hedge version is shown. Here, children can directly click on the screen themselves to indicate where the target is. For families that use a computer without touchscreen, the website presents the box version of the task. We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse. Therefore, we asked children to point to the screen. Caregivers were then asked to act as the "digital finger" of their children and click on the indicated box. In order to facilitate the translation of children's pointing and caregivers' clicking, we decided to implement this categorical version of the task.

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

# Results

# Discussion

@@

>>>>

# -- POSSIBLE ROUGH STRUCTURE -- 
# intro
## individual differences in dev psy
- reliable tasks: need variation, more trials

## exisiting tasks for social cognition
- wellman

## current goal
- standardized, easy to use, continuous

# methods (let's see whether we want this generic heading...)
## design of our task
- training trials (touch & fam together, click on visible balloon / visible target flight, voice over trials)
- test trials
- flexible: two versions, can also use discrete
- face value

- stimulus timing

## implementation / development
- JS, HTML, CSS
- parcel?!
- SVG: scalable
- webapp: portable across devices, flexible, no hard system requirements
- response collection: file format, variables saved (click responses)

## data processing
- workflow for collecting data
- pipeline? downloading server data into r, coverting coordinate systems

# does our task induce variation?
## participants: kiga & prolific vali
## procedure 
## results
- for hedge & box
- sanity check: developmental trajectory
- remote testing: online child sample as side note

# do we capture variation reliably?
## participants: relikiga & prolific reli
## results: 
- internal consistency?
- test-retest

# exploratory: external validity
## participants: subsample kiga & relikiga with questionnaire data
## results: 
- peer exposure (box & hedge combined?)

# discussion
## limitations
## future development / extending the task
# conclusion

\newpage
# Introduction 
Idea for an opener :)

@@

- individual differences in developmental psychology
- reliable tasks, variation needed, more trials
- existing tasks for social cognition: wellman
- goal of the current project

# Methods
## Design of our balloon finding task
- training trials (summarize touch & fam & voice over)
- test trials in detail
- two versions: continuous & discrete, flexible to use

## Stimuli
# TODO: cartoon style stimuli. engaging and for children and adults alike

An animal character (i.e., agent; sheep, monkey, or pig) is placed centrally in a window. A balloon (i.e., target; blue, green, yellow, or red) is located in front of them. The target then falls to the ground. The agent’s gaze tracks the movement of the target, that is, the pupils and iris of the agent move in a way that their center aligns with the center of the target. Participants were then asked to locate the target’s position on the screen.

# TODO: phrasing training trials
There are three different trial types, depending on the visual access to the target flight and end location. In *touch training* trials, participants have *full visual access* to the target flight and the target's end location. In *familiarization trials*, participants have *partial visual access*: they witness the target flight but cannot see the target's end location. In *test trials*, participants have *no visual access* to the target flight nor the end location. When partial or no information about the target location is accessible,  participants are expected to use the agent’s gaze as a cue.

## Implementation
- Parcel?
- benefits of our choices: easy to adapt, portable across devices, webapp: no installation needed
- response collection: file formats, information we save

Material is presented as an interactive web-app that is accessible for computers and tablets and runs on any web browser. The code is open-source (https://github.com/ccp-eva/gafo-demo) and a live demo version can be found under: https://ccp-odc.eva.mpg.de/gafo-demo/.

@@

## Data processing
- workflow server to R, converting coordinate systems
We used `r cite_r("r-references.bib")` for all our analyses.

# Does the balloon finding task induce variation?
## Participants: kiga & prolific vali
## Procedure
## Results
- for hedge & box
- sanity check: developmental trajectory
- remote testing: online child sample as side note

# Can we capture variation reliably?
## Participants: religa kiga & prolific reli
## Procedure: 14 ± 3 days
- what is different compared to variation? nr of trials, fixed order
## Results
- internal consistency
- test-retest

# Exploring the external validity of our task
## Participants: subset kiga & relikiga that filled out questionnaires
## Results
- peer exposure (hedge & box combined?)

# Discussion
## Limitations
## Future development / extending the task

# Conclusion

@@

## Procedure Remote Testing
In the beginning of the online study, families were invited to enter "our virtual institute" and were welcomed by an introductory video of the study leader, shortly describing the research background and further procedure. Then, caregivers were informed about data security and were asked for their informed consent. They were asked to enable the sound and seat their child centrally in front of their device. Subsequently, a brief demographic questionnaire was displayed, asking for (1) the total number of household members, (2) the number of children, (3) age of the other children, (4) whether the child was in day care, and if yes, (5) since when and (6) for how long on an average day. Before the study started, families were instructed how to setup their webcam and enable the recording permissions. Study participation was video recorded whenever possible in order to ensure that the answers were generated by the children themselves. 
Then, families were guided through the online study with pre-recorded audio instructions. After completion, families received a little crafting / coloring sheet as a small thank-you gift.

Depending on the participant's device, the website automatically presents the hedge or box version of the study. For families that use a tablet with touchscreen, the hedge version is shown. Here, children can directly click on the screen themselves to indicate where the target is. For families that use a computer without touchscreen, the website presents the box version of the task. We assumed that younger children in our sample would not be acquainted with the usage of a computer mouse. Therefore, we asked children to point to the screen. Caregivers were then asked to act as the "digital finger" of their children and click on the indicated box. In order to facilitate the translation of children's pointing and caregivers' clicking, we decided to implement this categorical version of the task.

### 2022-02-18 paper/manuscript.tex
create rough paper structure

@@

@@

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\hypertarget{material}{%
\subsection{Material}\label{material}}

@@

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

\hypertarget{remote-datacollection}{%
\subsubsection{Remote datacollection}\label{remote-datacollection}}

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

We used R {[}Version 4.1.2; R Core Team (2021){]} and the R-package \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]} for all our analyses.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

>>>>

\hypertarget{possible-rough-structure}{%
\section{-- POSSIBLE ROUGH STRUCTURE --}\label{possible-rough-structure}}

\hypertarget{intro}{%
\section{intro}\label{intro}}

\hypertarget{individual-differences-in-dev-psy}{%
\subsection{individual differences in dev psy}\label{individual-differences-in-dev-psy}}

\begin{itemize}
\tightlist
\item
  reliable tasks: need variation, more trials
\end{itemize}

\hypertarget{exisiting-tasks-for-social-cognition}{%
\subsection{exisiting tasks for social cognition}\label{exisiting-tasks-for-social-cognition}}

\begin{itemize}
\tightlist
\item
  wellman
\end{itemize}

\hypertarget{current-goal}{%
\subsection{current goal}\label{current-goal}}

\begin{itemize}
\tightlist
\item
  standardized, easy to use, continuous
\end{itemize}

\hypertarget{methods-lets-see-whether-we-want-this-generic-heading}{%
\section{methods (let's see whether we want this generic heading\ldots)}\label{methods-lets-see-whether-we-want-this-generic-heading}}

\hypertarget{design-of-our-task}{%
\subsection{design of our task}\label{design-of-our-task}}

\begin{itemize}
\item
  training trials (touch \& fam together, click on visible balloon / visible target flight, voice over trials)
\item
  test trials
\item
  flexible: two versions, can also use discrete
\item
  face value
\item
  stimulus timing
\end{itemize}

\hypertarget{implementation-development}{%
\subsection{implementation / development}\label{implementation-development}}

\begin{itemize}
\tightlist
\item
  JS, HTML, CSS
\item
  parcel?!
\item
  SVG: scalable
\item
  webapp: portable across devices, flexible, no hard system requirements
\item
  response collection: file format, variables saved (click responses)
\end{itemize}

\hypertarget{data-processing}{%
\subsection{data processing}\label{data-processing}}

\begin{itemize}
\tightlist
\item
  workflow for collecting data
\item
  pipeline? downloading server data into r, coverting coordinate systems
\end{itemize}

\hypertarget{does-our-task-induce-variation}{%
\section{does our task induce variation?}\label{does-our-task-induce-variation}}

\hypertarget{participants-kiga-prolific-vali}{%
\subsection{participants: kiga \& prolific vali}\label{participants-kiga-prolific-vali}}

\hypertarget{procedure}{%
\subsection{procedure}\label{procedure}}

\hypertarget{results}{%
\subsection{results}\label{results}}

\begin{itemize}
\tightlist
\item
  for hedge \& box
\item
  sanity check: developmental trajectory
\item
  remote testing: online child sample as side note
\end{itemize}

\hypertarget{do-we-capture-variation-reliably}{%
\section{do we capture variation reliably?}\label{do-we-capture-variation-reliably}}

\hypertarget{participants-relikiga-prolific-reli}{%
\subsection{participants: relikiga \& prolific reli}\label{participants-relikiga-prolific-reli}}

\hypertarget{results-1}{%
\subsection{results:}\label{results-1}}

\begin{itemize}
\tightlist
\item
  internal consistency?
\item
  test-retest
\end{itemize}

\hypertarget{exploratory-external-validity}{%
\section{exploratory: external validity}\label{exploratory-external-validity}}

\hypertarget{participants-subsample-kiga-relikiga-with-questionnaire-data}{%
\subsection{participants: subsample kiga \& relikiga with questionnaire data}\label{participants-subsample-kiga-relikiga-with-questionnaire-data}}

\hypertarget{results-2}{%
\subsection{results:}\label{results-2}}

\begin{itemize}
\tightlist
\item
  peer exposure (box \& hedge combined?)
\end{itemize}

\hypertarget{discussion}{%
\section{discussion}\label{discussion}}

\hypertarget{limitations}{%
\subsection{limitations}\label{limitations}}

\hypertarget{future-development-extending-the-task}{%
\subsection{future development / extending the task}\label{future-development-extending-the-task}}

\hypertarget{conclusion}{%
\section{conclusion}\label{conclusion}}

@@

\begin{itemize}
\tightlist
\item
  individual differences in developmental psychology
\item
  reliable tasks, variation needed, more trials
\item
  existing tasks for social cognition: wellman
\item
  goal of the current project
\end{itemize}

@@

\hypertarget{design-of-our-balloon-finding-task}{%
\subsection{Design of our balloon finding task}\label{design-of-our-balloon-finding-task}}

\begin{itemize}
\tightlist
\item
  training trials (summarize touch \& fam \& voice over)
\item
  test trials in detail
\item
  two versions: continuous \& discrete, flexible to use
\end{itemize}

\hypertarget{todo-cartoon-style-stimuli.-engaging-and-for-children-and-adults-alike}{%
\section{TODO: cartoon style stimuli. engaging and for children and adults alike}\label{todo-cartoon-style-stimuli.-engaging-and-for-children-and-adults-alike}}

\hypertarget{todo-phrasing-training-trials}{%
\section{TODO: phrasing training trials}\label{todo-phrasing-training-trials}}

\hypertarget{implementation}{%
\subsection{Implementation}\label{implementation}}

\begin{itemize}
\tightlist
\item
  Parcel?
\item
  benefits of our choices: easy to adapt, portable across devices, webapp: no installation needed
\item
  response collection: file formats, information we save
\end{itemize}

@@

\hypertarget{data-processing-1}{%
\subsection{Data processing}\label{data-processing-1}}

\begin{itemize}
\tightlist
\item
  workflow server to R, converting coordinate systems
  We used R {[}Version 4.1.2; R Core Team (2021){]} and the R-package \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]} for all our analyses.
\end{itemize}

\hypertarget{does-the-balloon-finding-task-induce-variation}{%
\section{Does the balloon finding task induce variation?}\label{does-the-balloon-finding-task-induce-variation}}

\hypertarget{participants-kiga-prolific-vali-1}{%
\subsection{Participants: kiga \& prolific vali}\label{participants-kiga-prolific-vali-1}}

\hypertarget{procedure-1}{%
\subsection{Procedure}\label{procedure-1}}

\hypertarget{results-3}{%
\subsection{Results}\label{results-3}}

\begin{itemize}
\tightlist
\item
  for hedge \& box
\item
  sanity check: developmental trajectory
\item
  remote testing: online child sample as side note
\end{itemize}

\hypertarget{can-we-capture-variation-reliably}{%
\section{Can we capture variation reliably?}\label{can-we-capture-variation-reliably}}

\hypertarget{participants-religa-kiga-prolific-reli}{%
\subsection{Participants: religa kiga \& prolific reli}\label{participants-religa-kiga-prolific-reli}}

\hypertarget{procedure-14-3-days}{%
\subsection{Procedure: 14 ± 3 days}\label{procedure-14-3-days}}

\begin{itemize}
\tightlist
\item
  what is different compared to variation? nr of trials, fixed order
  \#\# Results
\item
  internal consistency
\item
  test-retest
\end{itemize}

\hypertarget{exploring-the-external-validity-of-our-task}{%
\section{Exploring the external validity of our task}\label{exploring-the-external-validity-of-our-task}}

\hypertarget{participants-subset-kiga-relikiga-that-filled-out-questionnaires}{%
\subsection{Participants: subset kiga \& relikiga that filled out questionnaires}\label{participants-subset-kiga-relikiga-that-filled-out-questionnaires}}

\hypertarget{results-4}{%
\subsection{Results}\label{results-4}}

\begin{itemize}
\tightlist
\item
  peer exposure (hedge \& box combined?)
\end{itemize}

\hypertarget{discussion-1}{%
\section{Discussion}\label{discussion-1}}

\hypertarget{limitations-1}{%
\subsection{Limitations}\label{limitations-1}}

\hypertarget{future-development-extending-the-task-1}{%
\subsection{Future development / extending the task}\label{future-development-extending-the-task-1}}

\hypertarget{conclusion-1}{%
\section{Conclusion}\label{conclusion-1}}

@@

\hypertarget{procedure-remote-testing}{%
\subsection{Procedure Remote Testing}\label{procedure-remote-testing}}
